A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-23 manuscript.Rmd
add section on github

And you could commit it in Git:
<!--I am leaning towards doing everything in R, not sure though-->
<!--For Git we maybe should use RStudio's Git pane-->

@@

And Git can show you what has changed, like in Figure \@ref(fig:idea-change).

@@

Even when other researchers are excited to use your code or materials, they are usually legally inhibited from to doing so.
That is because in many countries (i.e. the USA) the creator of something has exclusive right to use their creation.
A license allows other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media, whereas scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com), however, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if their first contribution occurs after you have added a license, they give their consent by contributing.
To add a CC-BY license to your project simply run (there are similar commands for other licenses):

@@

GitHub/GitLab are great as a shared information basis: sharing and editing files, discussing and distributing tasks via issues and documenting the project via wikis even before data collection starts.

<!--Hands-on: Introduce Github-->

>>>>

And you could commit it in Git:
<!--I am leaning towards doing everything in R, not sure though-->
<!--For Git we maybe should use RStudio's Git pane?-->

@@

And GitHub can show you what has changed, like in Figure \@ref(fig:idea-change).
GitHub is in its essence a Webinterface to Git and you may learn more about how to use it under the section on [GitHub].

@@

Even when other researchers are excited to use your code or materials, they are usually legally inhibited from to doing so.
That is because in many countries (i.e. the USA, European Union) the creator of something has exclusive right to use their creation.
A license allows other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media, whereas scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com), however, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if their first contribution occurs after you have added a license, they give their consent by contributing.
To add a CC-BY license to your project simply run (there are similar commands for other licenses):

@@

On your local machine, you use Git to track changes.
However, to share these changes with others, you need to use an online service like GitHub.
GitHub is not the only solution; there is also GitLab or BitBucket, which are as feature-rich as GitHub.
GitLab has the advantage that your institution can host it themselves; therefore, you are not relying on commercial service providers.
We focus on GitHub because it is the most popular service.
To upload your changes to GitHub, you need to create an account under https://github.com/join.
As a researcher, you are eligible for the `r link("https://help.github.com/en/articles/applying-for-an-educator-or-researcher-discount", "Researcher/Educator discount").
The following command creates a new GitHub repository under your GitHub account, beware this is public:
<!--Hands-on: Introduce Github-->

To create a private repository (only you and people you invite have access), use:
